PubCrawl: A Paper Search Engine

### 2012-05-15 report/paper.tex
Added color/pic to presentation, expanded report

\begin{abstract}
Searching for documents ranked by relevance is a well-studied problem for web
pages. In particular, there are frameworks for estimating relevance as a
function of the content of the document and algorithms for estimating relevance
as a function of incoming links. However, further specialization of these
techniques is required to search a corpus of academic papers. Academic papers
are highly structured, lending additional weight to matches which appear in
important sections such as the title or abstract. Moreover, citations have
contextual information which changes the weight which should be contributed to
cited papers. Here we describe PubCrawl, a search engine built for the ACM
Digital Library. The system allows users to weight the relative importance of
matches in the title, abstract, full text, and the PageRank of each hit,
providing a platform to test further refinements of the algorithms. We evaluate
the system in user studies.
\end{abstract}

@@

\begin{figure}[t]
\centering
	\includegraphics[width=5in]{images/component-graph}
	\caption{Sizes of components in the ACM data set and the number of each size's occurrence.}	
	\label{comp-size}
\end{figure}

Components in the citation graph are the other source of complication. Papers in the same component are either both part of the same citation chain or share a common ancestor or descendant in their respective chain. The ACM data exhibits 45,571 total components, with one large component of 176,285 papers, and a large number of smaller components ranging in size from one to ten papers, as displayed in Figure \ref{comp-size}. Small components are papers that don't cite many or any other papers in the data set and aren't heavily cited. This implies that nodes in small components should not be highly ranked.

To adjust for this, nodes are categorized into the components they belong in. Instead of initializing node scores to be a constant value such as 1, they are instead initialized to a score linear to the size of the component containing the nodes. Intuitively, this means that papers in larger components will receive higher scores, as desired.

>>>>

@@

Components in the citation graph are the other source of complication. Papers in the same component are either both part of the same citation chain or share a common ancestor or descendant in their respective chain. The ACM data exhibits a large number (???? exact number????) of components, with a small number of large components and a large number of components with just a few papers (Figure ???). Small components are papers that don't cite any other papers in the data set and aren't heavily cited. This implies that nodes in small components should not be highly ranked. 
To adjust for this, nodes are categorized into the components they belong in. Instead of initializing node scores to be a constant value such as 1, they are instead initialized to a score linear to the size of the component containing the nodes. Intuitively, this means that papers in larger components will receive higher scores, as desired.
